### 2020-01-21 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: Made maths notation a bit clearer in Aura Calculation

To lower inconsistencies during migration, the following user-defined tolerances are used for the aura calculations: maximum speed; maximum latency time; maximum frame-time. If velocities, latencies, or frame-time are above these tolerances, then stability is no longer guaranteed. This enables AP to deterministically indicate to the overall simulation when latency may be influencing the mutually consistent views of the servers, which in turn manifests as errors in the physics.

>>>>

To lower inconsistencies during migration, the following user-defined tolerances are used for the aura calculations: 
\begin{itemize}
	\item $V_{t}$ - maximum speed of simulated objects.
	\item $T_{L}$ - maximum network latency time.
	\item $T_{F}$ - maximum frame-time (time allowed for combined frame update and network update).
\end{itemize}
If velocities, latencies, or frame-time are above these tolerances, then stability is no longer guaranteed. This enables AP to deterministically indicate to the overall simulation when latency may be influencing the mutually consistent views of the servers, which in turn manifests as errors in the physics.
